Supplementary Materials

### 2023-06-28 manuscript/supplementary.tex
supp cleanup

\renewcommand{\P}{\mathbb{P}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\V}{\text{V}}
\DeclareMathOperator{\var}{V}
\newcommand{\V}{\text{V}}
\DeclareMathOperator{\cov}{cov}

@@

\subsection{Sources of Neutral Allele Frequency Change}

@@

\begin{align}
    \label{eq:vardecay}
  \V(x_2 - p_0) &= \E({S_1}^2) + \E(S_1 S_2) + \E({S_2}^2) \nonumber \\
                  & + \E({D_1}^2) + \E({H_1}^2) + \E({D_2}^2) + \E({H_2}^2) \nonumber \\
  \frac{\V(x_2 - p_0)}{p_0(1-p_0)} &= \frac{V_A}{2N} + \frac{V_A Q_2^2}{2N}\left(1-\frac{1}{2N}\right)  +  \frac{V_A}{2N_}  \left(1-\frac{1}{2N}\right)  \nonumber \\ 
                                     &+ \frac{V_n}{8N} + \frac{1}{4N} + \frac{V_n}{8N}  \left(1 - \frac{1}{2N}\right) 
+ \frac{1}{4N} \left(1 - \frac{1}{2N}\right).
\end{align}
%
In general, the variance in allele frequency change after $t$ generations in a
system with heritable fitness due to a single locus $r$ recombination fraction
away from the neutral site is given by,

@@

Now, we consider how to turn this expression for the variance in neutral allele
frequency at time $t$ under weak draft into an expression for the
\emph{draft-effective} population size analogous to Supplementary Equation
\eqref{supp-eq:var-ne}. In an ideal Wright--Fisher population, the
instantaneous variance is $\V(\Delta x_t) =
\nicefrac{p_{t-1}(1-p_{t-1})}{2N_{d,t-1}}$. Santiago and Caballero consider the
allele frequency change at some $t$ to define their effective population size
at time $t$ (which we here are calling draft-effective population size,
$N_{d,t}$),

@@

\begin{align}
    N_d := \lim_{t \to \infty} N_{d,t} \approx \frac{4N}{4 V_A Q_\infty^2 +V_n+2}.
\end{align}

We now turn to different expressions for $Q_t^2$ and $V_A$.

@@

Our model differs from that of \textcite{Santiago1998-bs} in that we do not
integrate over the entire genome. In their 1998 model, Santiago and Caballero
consider the impact of both sites under selection on the same chromosome, as
well as sites on independently assorting chromosomes. We only consider the
contribution of a single segment under purifying selection, and the reduction
from additional segments accumulate multiplicatively. Like their model, we
imagine the reduction experienced by a focal neutral site in the middle of the
segment. The implementation of our method differs slightly on though, see XXX.

@@

\subsection{The Draft-Effective Population Size Under Weak and Strong BGS}
\label{supp:weak-strong}

@@

\begin{align}
  \label{supp-eq:Va}
  V_{A} = Us - 2Rs. 
\end{align}
%
where $U = 2u$ and $R=r$ is the diploid rate of the ratchet, which depends on
higher moments of the fitness distribution, but only differs from $r$ through a
rescaling of the population size. We also find that Equation \eqref{eq:Va} and
Supplementary Materials Equation \ref{supp-eq:Va} above can also be found
through Kimura's diffusion models with a flux of mutations into infinite,
discrete sites (\citeyear{Kimura1969-jw}). Note that if selected sites are
sufficiently deleterious that they cannot fix (or the population is infinite),
$R=0$ and the additive fitness variance is identical to that under strong
background selection, $V_A = Us = V_\text{BGS}$ (equation \ref{eq:va_bgs}).
We note that while we use $V_A$ here following \textcite{Santiago2016-mu}, 
this is only the \emph{additive genic} component of additive fitness variation,
as our simulations confirm in the main text.

@@

\begin{align}
  R(N_{d,\infty}) &= \frac{4 U s N_{d,\infty}}{\exp(4 N_{d,\infty} s)-1}\\
  N_{d,\infty} &\approx N \exp\left(-\frac{V_A}{(1-Z) (2-(2-M) Z)} \right)
\end{align}
%
The solution to these equations is the asymptotic equilibrium $\widetilde{N}_d$
and equilibrium ratchet rate $\widetilde{R}$. This sets the equilibrium
variance, $\widetilde{V} = Us - 2\widetilde{R}s$, or $\widetilde{V} = (U -
2\widetilde{R})s$. Note that because $p_\text{fix} < \nicefrac{1}{2N}$ for
deleterious variation, $2R < U$, or the diploid mutation rate must be greater
than or equal to twice the per-basepair per-generation substitution rate for
equilibrium variance $\widetilde{V} > 0$ for $s>0$.

@@

@@

Both classic BGS and the B' method we build off the SC16 model have the same
parametric form, since both (1) model the impact of linked selection as a
rescaling of effective population size, and (2) both assume multiplicative
fitness across segments. Thus, the total reduction experienced by a neutral
site at position $x$ due to segments across the genome is the product of the
individual reductions is

\begin{align}
  \label{supp-eq:b}
  B(x, \Psi) &= \prod_g^S \exp \left( \int_0^1 b(\mu(s, k(g)), s, L_g, r_g, d(x, g)) ds \right) \\
             &= \exp \left( \sum_g^S \int_0^1 b(\mu(s, k(g)), s, L_g, r_g, d(x, g)) ds \right)
\end{align}

where, $b(\mu(s, k(g)), s, L_g, r_g, d(x,g))$ is the log reduction due to
segment $g$, and there are $S$ total segments. Here, $\mu(s, k(g))$ is the
per-basepair per-genome rate that mutations with selection coefficient $s$
enter segments with feature class $k(g)$ (e.g. it incorporates the distribution
of fitness effects and mutation rate), $L_g$ and $r_g$ are the length in
basepairs and recombination rate per basepair of segment $g$, and the
recombination distance between focal site $x$ and segment $g$ is $d(x, g)$. The
functional form of $b$ varies depending on whether the classic BGS model is
used (Supplementary Section \ref{supp:reduction-classic}), or our form of
Santiago and Caballero's (\citeyear{Santiago2016-mu}) equations (see
Supplementary Section \ref{supp:reduction-sc16}).

Under both background selection models used in our likelihood, the diversity in
window $v$ is $\bar{\pi}(v, \Psi) = \bar{B}(v, \Psi) \pi_0$. Here, $\bar{B}(v |
\Psi)$ is the predicted reduction in diversity due to BGS in window $v$, given
background selection parameters $\Psi$. In practice, we pre-calculate $B(x |
\Psi)$ at fixed sites $x$ across the genome, and take the average of the fixed
sites $B$ values within window $v$ for the average $\bar{B}(v | \Psi)$.

\subsubsection{Reductions Under the Classic BGS Model}
\label{supp:reduction-classic}

The classic BGS model, which assumes deleterious mutations cannot fix,
expresses the reduction for a focal site in the middle of a segment
\parencite{Hudson1995-xc,Hudson1994-oh,Nordborg1996-nq}; here we consider a
focal site directly to an arbitrary side of a segment under a deleterious
mutations, and extend the model to handle a focal segment arbitrarily far from
the segment. To simplify notation, we will only consider a single feature class
in this and the next section. Using our notation from equation
\eqref{supp-eq:b}, the log reduction under the classic
mutation-selection-balance BGS model is,

\begin{align}
  b(\mu, s, L, r, 0) &=  - \int_0^L \frac{2\mu(l)}{s (1 + (1-s) r(l)/s)^2} dl 
\end{align}

(c.f. \cite{Hudson1995-xc} equation 5), where $\mu(l)$ is the \emph{haploid}
per-basepair mutation rate at $l$ and $r(l)$ is the recombination fraction
between the focal site (at position 0) and basepair $l$. Assuming constant
per-basepair recombination and mutation rates, $r(l) = r_\text{BP}l$ and
$\mu(l) = \mu$, and

\begin{align}
  b(\mu, s, L, r_\text{BP}, 0) &= - \frac{2\mu L}{s + (1-s) r_\text{BP} L} 
\end{align}

(c.f. \cite{Hudson1995-xc} equation 8, where the factor of two difference is
due to the position of the focal site). Often per-region rates are defined $U =
2 \mu L$ and $M = r_\text{BP} L$ are the segment-wide mutation diploid mutation
rates (mutations per diploid segment per generation) and recombination length
(Morgans).

For computational efficiency, we adjust this model by setting $r(l) = d +
r_\text{BP} l$, where $d$ is the recombination fraction between the focal site
$x$ and the start of segment $g$. This allows us to pre-compute the local
effects of the segment, and substitute in $b$ as the focal site changes. This
integral substitution has a closed form,

\begin{align}
  b(\mu, s, L, r_\text{BP}, d) &= \frac{-2\mu L}{(d(1-s) + s)(s + (d + r_\text{BP}L)(1-s))}
\end{align}

and terms can be collected in powers of $d$ and pre-computed for all segments
for the grid of $\mu$ and $s$. Our implementation pre-computes these segment
components, and computes the final $b$ value for an $x$ and $g$ by calculating
the distance $d(x,g) = |M(x) - M(g)|$, where $M(x)$ is the cumulative
recombination map length at position $x$ in Morgans. Since $r(l)$ could vary by
position, segments with differing recombination rates are split into segments
of the same annotation class by their recombination rate. This has no effect on
the calculation due to the multiplicative fitness, but ensures more accurate
estimates of the reduction factor $B$.

@@

\subsubsection{Reduction Under the Modified Santiago and Caballero Model}
\label{supp:reduction-sc16}

Under Santiago and Caballero's model, the correct effective population size to
gauge reduction in heterozygosity or coalescent times is given by their
equation 4 \parencite{Santiago2016-mu}. This equation considers how the
inflation factor $Q_t^2$ that sets the draft-effective population size varies
over $t$ (c.f. Supplementary equation \ref{eq:net_integral}). This is because
selective processes can lead to non-constant pairwise coalescent rates, which
impact pairwise coalescent rates and thus the reduction factor. We experimented
with calculating this full sum and integral approximations to it in our
methods, but it seemed to make little difference in our application.
Additionally, it was too costly to calculate computationally for genome-wide
calculations of the B' map. Instead, we solve for the asymptotic
$\widetilde{N}_{e,\infty}$ for each segment, and use that to calculate the log
reduction factor under the SC16 model, $b'$.

Note that the asymptotic model above determines the reduction in effective
population size experienced by a focal site in the middle of a $L$-basepair
segment, but B maps require the reduction $b'$ experienced by a focal site $x$
at an arbitrary recombination distance apart. For each segment, we pre-compute
the solution to the system of two equations, giving us $V$ and $Q_\infty^2$,
and then use these values in the equation \eqref{eqn:Ne_VQ2},

\begin{align} 
    b'(\mu, s, L, r, d) = -\frac{V}{2} \left(\frac{1}{(1-(1-d)Z}\right)^2 
\end{align}

where $Z = 1 - Us / (U-\widetilde{R})$ and $V = Us - 2\widetilde{R}s$. TODO
check d.

In practice, to fit such a model, we must discretize both $\mu(s, k(g))$ and
$s$ in Equation \eqref{supp-eq:b}. We define $\mu_i$ to be the rate of
mutations entering the population per basepair, per generation with selection
coefficient $s_i$ (i.e. the product of the mutation rate and the distribution
of deleterious fitness effects). Then, the reduction at position $x$ is,

\begin{align}
  \label{supp-eq:b}
  B(x, \Psi) = \exp \left( \sum_g^S \sum_{i} b\left( \mu_{i, \;k(g)}, s_i, L_g, r_g, d(x, g) \right)\right).
\end{align}

%TODO double check

Because it is computationally-intensive to numerically solve the system of two
non-linear equations to calculate $b$ at each segment, these are pre-computed
for an $m_s$-element grid of selection coefficients and an $m_\mu$-element grid
of mutation rates--DFE products. The number of annotation features $K$ is
variable and set by the annotation data specified. There are two ways to
parameterize the mutation rates and DFE for all annotation classes in
background selection models. First, for the \emph{free-mutation}
parameterization, each annotation feature class has a free mutation rate
parameter for each of these selection coefficients (as in equation
\eqref{supp-eq:b}).

In the free-mutation parameterization, there are $1 + K \times m_s$ for $\pi_0$
and the free mutation rate parameters, where $K$ is the number of annotation
features. The MLE optimization for this approach is unconstrained, though
$\pi_0$ is bounded to be within $10^{-5} \le \pi_0 \le 10^{-1}$ and mutation
rates are bounded within $10^{-11} \le \mu \le 10^{-7}$. The BGS model requires
a mutation rate for each selection coefficient in the grid, for each annotation
class (here, as an example, CDS, UTRs, and phastcons), which are stored in the
$m_s \times K$ matrix $\mathbf{M}_\text{F}$,

\begin{align}
  \mathbf{M}_\text{F} = \begin{bmatrix}
    \mu_{10^{-6},\text{CDS}} & \mu_{10^{-6},\text{UTR}} & \mu_{10^{-6},\text{PC}} \\
    \mu_{10^{-5},\text{CDS}} & \mu_{10^{-5},\text{UTR}} & \mu_{10^{-5},\text{PC}} \\
    \vdots & \vdots & \vdots \\
    \mu_{10^{-1},\text{CDS}} & \mu_{10^{-1},\text{UTR}} & \mu_{10^{-1},\text{PC}} \\
  \end{bmatrix}
\end{align}

That is, the distribution of fitness effect (DFE) is implied by
the total mutation rate across selection coefficients for an annotation class.
We can normalize by the total mutation rate estimate to get the estimated DFE,
giving us the DFE weight for annotation class $k$ and selection coefficient
with index $i$,

\begin{align}
  \widehat{w}_{i,k} = \frac{\widehat{\mu}_{i,k}}{\sum_i \widehat{\mu}_{i,k}}.
\end{align}

The second parametrization is the \emph{simplex} parametrization, which has a
single mutation rate across all features, so it is a DFE weight matrix times
the mutation rate $\mu$,

\begin{align}
  \mathbf{M}_\text{S} = \mu \begin{bmatrix}
    w_{10^{-6},\text{CDS}} & w_{10^{-6},\text{UTR}} & w_{10^{-6},\text{PC}} \\
    w_{10^{-5},\text{CDS}} & w_{10^{-5},\text{UTR}} & w_{10^{-5},\text{PC}} \\
    \vdots & \vdots & \vdots \\
    w_{10^{-1},\text{CDS}} & w_{10^{-1},\text{UTR}} & w_{10^{-1},\text{PC}} \\
  \end{bmatrix}
\end{align}

which has $2 + K \times (m_s-1)$ free parameters, since each column must sum to
one. This imposes the constraint that $\sum_i w_{i,k} = 1$, requiring
constrained MLE optimization.

@@

\subsection{Numeric Optimization}

>>>>

\renewcommand{\P}{\mathbb{P}}
\newcommand{\E}{\mathbb{E}}
\DeclareMathOperator{\var}{V}
\newcommand{\V}{\text{V}}
\DeclareMathOperator{\cov}{cov}

@@

\subsection{Stochastic Sources of Neutral Allele Frequency Change}

@@

\begin{align}
    \label{eq:vardecay}
  \V(x_2 - p_0) &= \E({S_1}^2) + \E(S_1 S_2) + \E({S_2}^2) \nonumber \\
                  & + \E({D_1}^2) + \E({H_1}^2) + \E({D_2}^2) + \E({H_2}^2) \nonumber \\
  \frac{\V(x_2 - p_0)}{p_0(1-p_0)} &= \frac{V_A}{2N} + \frac{V_A Q_2^2}{2N}\left(1-\frac{1}{2N}\right)  +  \frac{V_A}{2N}  \left(1-\frac{1}{2N}\right)  \nonumber \\ 
                                     &+ \frac{V_n}{8N} + \frac{1}{4N} + \frac{V_n}{8N}  \left(1 - \frac{1}{2N}\right) 
+ \frac{1}{4N} \left(1 - \frac{1}{2N}\right).
\end{align}
%
In general, the variance in allele frequency change after $t$ generations in a
system with heritable fitness due to a single locus $r$ recombination fraction
away from the neutral site is given by,

@@

Now, we consider how to turn this expression for the variance in neutral allele
frequency at time $t$ under weak draft into an expression for the
\emph{draft-effective} population size analogous to drift-effective population
size given in Supplementary Equation \eqref{supp-eq:var-ne}. In an ideal
Wright--Fisher population, the instantaneous variance is $\V(\Delta x_t) =
\nicefrac{p_{t-1}(1-p_{t-1})}{2N_{d,t-1}}$. Santiago and Caballero consider the
allele frequency change at some $t$ to define their effective population size
at time $t$ (which we here are calling draft-effective population size,
$N_{d,t}$),

@@

\begin{align}
    N_d := \lim_{t \to \infty} N_{d,t} \approx \frac{4N}{4 V_A Q_\infty^2 +V_n+2}.
\end{align}
%
Now, we turn to different expressions for $Q_t^2$ and $V_A$ under different
types of polygenic selection.

@@

Our model differs from that of \textcite{Santiago1998-bs} in that we do not
integrate over the entire genome. In their 1998 model, Santiago and Caballero
consider the impact of both sites under selection on the same chromosome, as
well as sites on independently assorting chromosomes. We only consider the
contribution of a single segment under purifying selection, and the reduction
from additional segments accumulate multiplicatively. Like their model, we
imagine the reduction experienced by a focal neutral site in the middle of the
segment.

@@

\subsection{The Draft-Effective Population Size Under Weak and Strong Negative Selection}
\label{supp:weak-strong}

@@

\begin{align}
  \label{supp-eq:Va}
  V_{A} = Us - 2Rs. 
\end{align}
%
where $U = 2u$ and $R=r$ is the diploid rate of the ratchet, which depends on
higher moments of the fitness distribution, but only differs from $r$ through a
rescaling of the population size. We also find that Equation \eqref{eq:Va} and
Supplementary Equation \ref{supp-eq:Va} above can also be found
through Kimura's diffusion models with a flux of mutations into infinite,
discrete sites (\citeyear{Kimura1969-jw}). Note that if selected sites are
sufficiently deleterious that they cannot fix (or the population is infinite),
$R=0$ and the additive fitness variance is identical to that under strong
background selection, $V_A = Us = V_\text{BGS}$ (equation \ref{eq:va_bgs}).
We note that while we use $V_A$ here following \textcite{Santiago2016-mu}, 
this is only the \emph{additive genic} component of additive fitness variation,
as our simulations confirm in the main text.

@@

\begin{align}
    \label{supp-eq:sc16-sys}
  R(N_{d,\infty}) &= \frac{4 U s N_{d,\infty}}{\exp(4 N_{d,\infty} s)-1}\\
  N_{d,\infty} &\approx N \exp\left(-\frac{V_A}{(1-Z) (2-(2-M) Z)} \right)
\end{align}
%
The solution to these equations is the asymptotic equilibrium $\widetilde{N}_d$
and equilibrium ratchet rate $\widetilde{R}$. This sets the equilibrium
variance, $\widetilde{V} = Us - 2\widetilde{R}s$, or $\widetilde{V} = (U -
2\widetilde{R})s$. Note that because $p_\text{fix} < \nicefrac{1}{2N}$ for
deleterious variation, $2R < U$, or the diploid mutation rate must be greater
than or equal to twice the per-basepair per-generation substitution rate for
equilibrium variance $\widetilde{V} > 0$ for $s>0$.

@@

The previous section outlined the basis of quantitative genetic linked
selection models that predict the draft-effective population size under
polygenic selection and linkage. Our work here only considers the contribution
of strongly and weakly deleterious mutations to fitness variation. In this
section, we outline more details about the statistical models used to construct
the genome-wide B and B' maps that are used in model fitting.

@@

Both the classic BGS and the SC16 model we extend have the same parametric
form, since both (1) model the impact of linked selection as a rescaling of
effective population size, and (2) both assume multiplicative fitness across
segments. Thus, the total reduction experienced by a neutral site at position
$x$ due to segments across the genome is the product of the individual
reductions,

\begin{align}
  \label{supp-eq:b}
  B(x, \Psi) &= \prod_g^S \exp \left( \int_0^1 b(\mu(s, k(g)), s, L_g, r_g, d(x, g)) ds \right) \nonumber  \\
             &= \exp \left( \sum_g^S \int_0^1 b(\mu(s, k(g)), s, L_g, r_g, d(x, g)) ds \right)
\end{align}
%
where, $b(\mu(s, k(g)), s, L_g, r_g, d(x,g))$ is the log reduction due to
segment $g$, and there are $S$ total segments. Here, $\mu(s, k(g))$ is the
per-basepair per-genome rate that mutations with selection coefficient $s$
enter segments with feature class $k(g)$ (e.g. it incorporates the distribution
of fitness effects and mutation rate), $L_g$ and $r_g$ are the length in
basepairs and recombination rate per basepair of segment $g$, and the
recombination distance between focal site $x$ and segment $g$ is $d(x, g)$. The
functional form of $b$ varies depending on whether the classic BGS model is
used (Supplementary Section \ref{supp:reduction-classic}), or our form of
Santiago and Caballero's (\citeyear{Santiago2016-mu}) equations (see
Supplementary Section \ref{supp:reduction-sc16}).

Under both negative selection models implemented in our software, the diversity
in window $v$ is $\bar{\pi}(v, \Psi) = \bar{B}(v, \Psi) \pi_0$. Here,
$\bar{B}(v | \Psi)$ is the predicted reduction in diversity due to BGS in
window $v$, given background selection parameters $\Psi$. In practice, we
pre-calculate $B(x | \Psi)$ at fixed sites $x$ across the genome, and take the
average of the fixed sites $B$ values within window $v$ for the average
$\bar{B}(v | \Psi)$.

In practice, to fit negative selection models, we must discretize both $\mu(s,
k(g))$ and $s$ in Supplementary Equation \eqref{supp-eq:b}. We define
$\mu_{i,k(g)}$ to be the rate of mutations entering the population per basepair
per generation with selection coefficient $s_i$ for the feature class $k(g)$ of
segment $g$. This $\mu_{i, k(g)}$ term reflects the product of the mutation
rate and the distribution of deleterious fitness effects for selection
coefficient $s_i$ and feature class $k(g)$. Then, the reduction at position $x$
is,

\begin{align}
  \label{supp-eq:b-disc}
  B(x, \Psi) = \exp \left( \sum_g^S \sum_{i}^{m_s} b(\mu_{i, \;k(g)}, s_i, L_g, r_g, d(x, g))\right).
\end{align}
%
Because it is computationally-intensive to numerically solve the system of two
non-linear equations to calculate $b$ at each segment, these are pre-computed
for an $m_s$-element grid of selection coefficients and an $m_\mu$-element grid
of mutation rates--DFE products. Likewise, when we calculate $b$ under classic
BGS models, we pre-calculate segment components across these same grids, and
combine them for each $x$.

The number of annotation features $K$ is variable and set by the annotation
data specified. There are two ways to parameterize the mutation rates and DFE
for all annotation classes in background selection models. First, for the
\emph{free-mutation} parameterization, each annotation feature class has a free
mutation rate parameter for each of these selection coefficients (as in
Supplementary Equation \ref{supp-eq:b}). We experimented with this approach,
but ultimately found its results less intuitive and it has more degrees of
freedom.

% In the free-mutation parameterization, there are $1 + K \times m_s$ for $\pi_0$
% and the free mutation rate parameters, where $K$ is the number of annotation
% features. The MLE optimization for this approach is unconstrained, though
% $\pi_0$ is bounded to be within $10^{-5} \le \pi_0 \le 10^{-1}$ and mutation
% rates are bounded within $10^{-11} \le \mu \le 10^{-7}$. The BGS model requires
% a mutation rate for each selection coefficient in the grid, for each annotation
% class (here, as an example, CDS, UTRs, and phastcons), which are stored in the
% $m_s \times K$ matrix $\mathbf{M}_\text{F}$,

% \begin{align}
%   \mathbf{M}_\text{F} = \begin{bmatrix}
%     \mu_{10^{-6},\text{CDS}} & \mu_{10^{-6},\text{UTR}} & \mu_{10^{-6},\text{PC}} \\
%     \mu_{10^{-5},\text{CDS}} & \mu_{10^{-5},\text{UTR}} & \mu_{10^{-5},\text{PC}} \\
%     \vdots & \vdots & \vdots \\
%     \mu_{10^{-1},\text{CDS}} & \mu_{10^{-1},\text{UTR}} & \mu_{10^{-1},\text{PC}} \\
%   \end{bmatrix}
% \end{align}

% That is, the distribution of fitness effect (DFE) is implied by
% the total mutation rate across selection coefficients for an annotation class.
% We can normalize by the total mutation rate estimate to get the estimated DFE,
% giving us the DFE weight for annotation class $k$ and selection coefficient
% with index $i$,

% \begin{align}
%   \widehat{w}_{i,k} = \frac{\widehat{\mu}_{i,k}}{\sum_i \widehat{\mu}_{i,k}}.
% \end{align}

Instead, we opted for a \emph{simplex} parameterization, which has a single
shared mutation rate across all features, so the mutation parameter $\mu_{i,
\;k(g)}$ above is given by the product of the mutation rate and the DFE weight
matrix. For example, for a $\log_{10}$ selection grid and three features, CDS,
UTRs, and PhastCons (PC), we'd have a DFE matrix like,

\begin{align}
  \mathbf{M}_\text{S} = \mu \begin{bmatrix}
    w_{10^{-6},\text{CDS}} & w_{10^{-6},\text{UTR}} & w_{10^{-6},\text{PC}} \\
    w_{10^{-5},\text{CDS}} & w_{10^{-5},\text{UTR}} & w_{10^{-5},\text{PC}} \\
    \vdots & \vdots & \vdots \\
    w_{10^{-1},\text{CDS}} & w_{10^{-1},\text{UTR}} & w_{10^{-1},\text{PC}} \\
  \end{bmatrix}
\end{align}
%
which has $2 + K \times (m_s-1)$ free parameters, since each column must sum to
one. This imposes the constraint that $\sum_i w_{i,k} = 1$, requiring
constrained MLE optimization. We implement this using softmax, which describe 
further in Supplementary Section \ref{supp:optim}.

\subsection{Reductions Under the Classic BGS Model}
\label{supp:reduction-classic}

The classic BGS model, which assumes deleterious mutations cannot fix,
expresses the reduction for a focal site in the middle of a segment
\parencite{Hudson1995-xc,Hudson1994-oh,Nordborg1996-nq}; here we consider a
focal site directly to an arbitrary side of a segment under a deleterious
mutations, and extend the model to handle a focal segment arbitrarily far from
the segment. To simplify notation, we will only consider a single feature class
in this and the next section. The log reduction under the classic
mutation-selection-balance BGS model is,

\begin{align}
    \label{supp-eq:classic-b-int}
  b(\mu, s, L, r, 0) &=  - \int_0^L \frac{\mu(l)}{s (1 + (1-s) r(l)/s)^2} dl 
\end{align}
% 
(c.f. \cite{McVicker2009-ax} p. 11, \cite{Hudson1995-xc} equation 5,), where
$\mu(l)$ is the \emph{haploid} per-basepair mutation rate at $l$ and $r(l)$ is
the recombination fraction between the focal site (at position 0) and basepair
$l$. Assuming constant per-basepair recombination and mutation rates, $r(l) =
r_\text{BP}l$ and $\mu(l) = \mu$,

\begin{align}
  b(\mu, s, L, r_\text{BP}, 0) &= - \frac{\mu L}{s + (1-s) r_\text{BP} L} 
\end{align}
%
(c.f. \cite{Hudson1995-xc} equation 8; their model considers a neutral site in
the middle of the segment and drops small terms). Often per-region rates are
defined $U = 2 \mu L$ and $M = r_\text{BP} L$ are the segment-wide mutation
diploid mutation rates (mutations per diploid segment per generation) and
recombination length (Morgans).

For computational efficiency, we adjust this model by setting $r(l) = d +
r_\text{BP} l$ in Supplementary Equation \eqref{supp-eq:classic-b-int} and
integrating, where $d$ is the recombination fraction between the focal site $x$
and the start of segment $g$. This allows us to pre-compute the local effects
of the segment, and substitute in $b$ as the focal site changes. This integral
substitution has a closed form,

\begin{align}
  b(\mu, s, L, r_\text{BP}, d) &= - \frac{\mu L}{(d(1-s) + s)(s + (d + r_\text{BP}L)(1-s))}.
\end{align}
%
Then, terms can be collected in powers of $d$ and pre-computed for all segments for
the grid of $\mu$ and $s$. Our implementation of classic BGS in \texttt{bgspy}
pre-computes these segment components, and then calculates the final $b$ value
for an $x$ and $g$ by calculating the distance $d(x,g) = |M(x) - M(g)|$, where
$M(x)$ is the cumulative recombination map length at position $x$ in Morgans.
Since $r(l)$ could vary by position, segments with differing recombination
rates are split in two of the same annotation class by their recombination
rate. This has no effect on the calculation due to the multiplicative fitness,
but ensures more accurate estimates of the reduction factor $B$.

@@

\subsection{Reduction Under the Modified Santiago and Caballero Model}
\label{supp:reduction-sc16}

Under Santiago and Caballero's model, the correct effective population size to
gauge reduction in heterozygosity or coalescent times is given by their
equation 4 \parencite{Santiago2016-mu}. This equation considers how the
inflation factor $Q_t^2$ that sets the draft-effective population size varies
over $t$. This is because selective processes can lead to non-constant pairwise
coalescent rates, which impact pairwise coalescent rates and thus the reduction
factor. We experimented with calculating this full sum and integral
approximations to it in our methods, but it seemed to make little difference in
our application. Additionally, it was too costly to calculate computationally
for genome-wide calculations of the B' map. Instead, we solve for the
asymptotic $\widetilde{N}_{e,\infty}$ for each segment, and use that to
calculate the log reduction factor under the SC16 model, $b'$.

Note that the asymptotic model above determines the reduction in effective
population size experienced by a focal site in the middle of a $L$-basepair
segment, but B maps require the reduction $b'$ experienced by a focal site $x$
at an arbitrary recombination distance apart. For each segment, we pre-compute
the solution to the system of two equations in Supplementary Equation
\eqref{supp-eq:sc16-sys} for the mutation and selection coefficient grids,
giving us $\widetilde{V}$ and $\widetilde{Q}_\infty^2$ for each set of
parameters. Then,

\begin{align} 
    b'(\mu, s, L, r, d) = -\frac{\widetilde{V}}{2} \left(\frac{1}{(1-(1-d)Z}\right)^2 
\end{align}
%
where $Z = 1 - Us / (U-\widetilde{R})$ and $\widetilde{V} = Us - 2\widetilde{R}s$. As
before, $d$ is the recombination fraction between the segment and the focal
neutral site.

@@

\subsection{Numeric Optimization}
\label{supp:optim}
